class: bg-main1 split-30 hide-slide-number

.column.bg-main3[
]
.column.slide-in-right[
.sliderbox.bg-main2.vmiddle[
.font5[Introduction]
]]

---

class: middle center bg-main1

# What is .text-hl[Data Linkage]?

--

<br>
## It is a method used to gather .text-hl[information] from 
## .text-hl[different sources], giving rise to .text-hl[richer datasets]

---

class: middle center bg-main2

# What is .text-hl[Spatial Join]?

--

<br>
## It is a .text-hl[GIS] operation used to .text-hl[combine information] 
## from different sources of .text-hl[spatial data] based on a given
## relationship between their spatial features

---

class: split-two

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
]]
]]

.column.bg-main5[.content.vmiddle.center[
`r icon::fa_question(size = 5)`
]]

---

class: split-two fade-row2-col1 fade-row3-col1
count: false

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
## Polygons `r icon::fa_arrow_left()` Polygons
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
]]
]]
.column.bg-white[.content.vmiddle.center[
```{r int_im1, echo = F, eval = T, fig.width = 5}
sq1 + sq2 # + plot_layout(ncol = 1)
```
]]

---

class: split-two fade-row2-col1 fade-row3-col1
count: false

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
## Polygons `r icon::fa_arrow_left()` Polygons
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
]]
]]
.column.bg-white[.content.vmiddle.center[
```{r int_im2, echo = F, eval = T, fig.width = 5}
sq12
```
]]

---

class: split-two fade-row1-col1 fade-row3-col1
count: false

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
## Polygons `r icon::fa_arrow_left()` Polygons
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
## Polygons `r icon::fa_arrow_left()` Points 
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
]]
]]

.column.bg-white[.content.vmiddle.center[
```{r int_im3, echo = F, eval = T, fig.width = 5}
sq1 + pts1
```
]]

---

class: split-two fade-row1-col1 fade-row3-col1
count: false

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
## Polygons `r icon::fa_arrow_left()` Polygons
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
## Polygons `r icon::fa_arrow_left()` Points 
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
]]
]]

.column.bg-white[.content.vmiddle.center[
```{r int_im4, echo = F, eval = T, fig.width = 5}
sq1pt
```
]]

---

class: split-two fade-row1-col1 fade-row2-col1
count: false

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
## Polygons `r icon::fa_arrow_left()` Polygons
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
## Polygons `r icon::fa_arrow_left()` Points 
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
## Points `r icon::fa_arrow_left()` Polygons
]]
]]

.column.bg-white[.content.vmiddle.center[
```{r int_im5, echo = F, eval = T, fig.width = 5}
ptsq1
```
]]

---

class: split-two fade-row1-col1 fade-row2-col1
count: false

.column.bg-main1[
.split-three[
.row.bg-main1[.content.vmiddle.center[
# Example 1
## Polygons `r icon::fa_arrow_left()` Polygons
]]
.row.bg-main2[.content.vmiddle.center[
# Example 2
## Polygons `r icon::fa_arrow_left()` Points 
]]
.row.bg-main3[.content.vmiddle.center[
# Example 3
## Points `r icon::fa_arrow_left()` Polygons
]]
]]

.column.bg-main5[.content.vmiddle.center[
`r icon::fa_question(size = 5)`
]]

---